\mireval{}

### 2014-05-08 paper/paper.tex
Fixing table
Somehow the old table found it's way back in.  Also adding in rough draft of segment diff section

\begin{table*}[htb]
\label{tab:comparison}
  \centering
\begin{tabularx}{\linewidth}{c *{8}{>{\centering\arraybackslash}X}}
\toprule
 \multicolumn{9}{ c }{Beat Detection} \\
  \cmidrule(lr){1-9}
F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{c c c c c *{4}{>{\centering\arraybackslash}X}}
 \multicolumn{9}{ c }{Structural Segmentation} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{8}{>{\centering\arraybackslash}X}}
 \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c c c c c c c c}
 \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
 0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \bottomrule
\end{tabularx}
\end{table*}

@@

Brian writes this section, which covers the differences in beat.f\_measure, boundary.detection, and onset.f\_measure

@@

\subsection{Other segmentation differences}

Brian renames this section and writes it/splits it into different sections.

\subsection{Chord stuff}

Eric renames this section and writes it/splits it into different sections

@@

When a reference melody annotation contains no unvoiced frames, the voicing false alarm rate is not well defined.
MIREX assigns a score of 1 in this case, while \mireval{} assigns a score of 0.
%%%
%%%
%%%
% WHY?
%%%
%%%
%%%
In the data set over which the average relative change for the melody metrics was computed, one reference annotation contained no unvoiced frames.
This discrepancy caused a large inflation of the average relative change reported for the voicing false alarm rate.

@@

% Beat: Compared against MIREX 2013
% Segmentation: Compared against ??
% Melody: Compared against MIREX 2011, SG2 only
% Pattern: Compared against development set, MATLAB code
% Source Separation: Compared against SiSEC dev sets
% Onset: Compared against MIREX 2013

% Beat - 9 metrics
% Chord - 5 metrics
% Segmentation - 14 metrics
% Melody - 5 metrics
% Pattern - 21 metrics
% Onset - 3 metrics
% Source Separation - 3 metrics

\begin{table*}[t]
  \centering
\begin{tabular}{c c c c c c c c c c}

\toprule
 \multicolumn{5}{ c }{Chord} & \multicolumn{5}{ c }{Melody}\\
  \cmidrule(lr){1-5}

  \cmidrule(lr){5-10}
 Root & M/m & M/m + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Raw Chroma & Voicing R & Voicing F-A\\
  0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \midrule
 \multicolumn{10}{ c }{Segmentation} \\
  \cmidrule(lr){1-10}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5       & F@3 \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\% &    0.393\% \\
  \midrule
 \multicolumn{4}{ c }{Segmentation} & \multicolumn{6}{ c }{Beat}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-10}
  P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt \\
  0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% \\
  \midrule
 \multicolumn{3}{ c }{Beat} & \multicolumn{7}{ c }{Pattern}\\
  \cmidrule(lr){1-3}
  \cmidrule(lr){4-10}
  AMLc       & AMLt       & In. Gain & Pat & Pat & Pat & Pat & Pat & Pat & Pat \\
  0.137\% &    0.139\% &   9.174\% &  ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{10}{ c }{Pattern}\\
  \cmidrule(lr){1-10}
  Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat & Pat\\
  ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ??? & ???\\
  \midrule
 \multicolumn{4}{ c }{Pattern}  & \multicolumn{3}{ c }{Onset}  & \multicolumn{3}{ c }{Source Separation}\\
  \cmidrule(lr){1-4}
  \cmidrule(lr){5-7}
  \cmidrule(lr){8-10}
 Pat & Pat & Pat & Pat & F-measure  & Precision  & Recall & SDR & SIR & SAR \\
 ??? & ??? & ??? & ??? &    0.165\% &    0.165\% &    0.165\% & ??? & ??? & ??? \\
  \bottomrule

\end{tabular}
\label{table:comparisons}
\end{table*}
>>>>>>> 63bc147b652a8ff4fcd68d1cd3b1f2b0889cb07b

>>>>

\begin{table*}[htb]
\label{tab:comparison}
  \centering
\begin{tabularx}{\linewidth}{c *{8}{>{\centering\arraybackslash}X}}
\toprule
 \multicolumn{9}{ c }{Beat Detection} \\
  \cmidrule(lr){1-9}
F-Measure  & Cemgil     & Goto       &  P-score   & CMLc       & CMLt       & AMLc       & AMLt       & In. Gain   \\
   0.703\% &    0.035\% &    0.054\% &    0.877\% &    0.161\% &    0.143\% &    0.137\% &    0.139\% &    9.174\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{c c c c c *{4}{>{\centering\arraybackslash}X}}
 \multicolumn{9}{ c }{Structural Segmentation} \\
  \cmidrule(lr){1-9}
  NCE-Over   & NCE-under  & Pairwise F & Pairwise P & Pairwise R & Rand       & F@.5       & P@.5       & R@.5  \\
3.182\% &   11.082\% &    0.937\% &    0.942\% &    0.785\% &    0.291\% &    0.429\% &    0.088\% &    1.021\%  \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{8}{>{\centering\arraybackslash}X}}
 \multicolumn{5}{ c }{Structural Segmentation (continued)} & \multicolumn{3}{ c }{Onset Detection}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-8}
  F@3 &   P@3        & R@3 & Ref-est dev. & Est-ref dev. & F-measure  & Precision  & Recall     \\
 0.393\%  & 0.094\% &    0.954\% & 0.935\% &    0.000\% &  0.165\% &    0.165\% &    0.165\% \\
  \midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{*{2}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c *{1}{>{\centering\arraybackslash}X} c c}
 \multicolumn{5}{ c }{Chord Recognition} & \multicolumn{5}{ c }{Melody Extraction}\\
  \cmidrule(lr){1-5}
  \cmidrule(lr){6-10}
  Root       & Maj/min       & Maj/min + Inv & 7ths & 7ths + Inv & Overall & Raw Pitch & Chroma & Voicing R & Voicing FA \\
 0.007\% & 0.1634\% & 1.005\% & 0.483\% & 0.899\% & 0.070\% &    0.087\% &    0.114\% &    0.000\% &   10.095\% \\
  \bottomrule
\end{tabularx}
\end{table*}

@@

In the computation of the F-measure, precision and recall metrics for the beat tracking, boundary detection, and onset detection tasks, an estimated event is considered correct (a ``hit'') if it falls within a small window of a reference event.
No estimated boundary is counted as a hit for more than one reference boundary, and vice versa.
In MIREX, this assignment is done in a greedy fashion, however in \mireval{} we use an optimal matching strategy.
This is accomplished by computing a maximum bipartite matching between the estimated events and the reference events (subject to the window constraint) using the Hopcroft-Karp algorithm~\cite{hopcroft1973n}.
This explains the observed discrepancy between \mireval{} and MIREX for each of these metrics.
In all cases where the metric differs, \mireval{} reports a higher score, indicating that the greedy matching strategy was suboptimal.

\subsection{Segment Boundary Deviation}

% Because when numpy computes the median of an even number of numbers, it computes the mean of the two middle values.

\subsection{Segment Frame Clustering}

% Frame sampling - MIREX does two different things, we do one thing consistently
% For Rand index and pairwise classification, MIREX uses a fixed sampling but at different rates.
% In the conditional entropy scores, it uses a fixed number of samples.
% In \mireval{}, we use the same fixed sampling rate for all metrics.

% In MIREX, the range over which frames are sampled depends on both the reference and the estimate intervals.
% In \mireval{}, the sampling is always done with respect to the reference to ensure fair comparison across multiple estimates for the same reference.

% This additionally requires that estimated intervals are adjusted to span the exact duration specified by the reference intervals.
% In \mireval{}, this is done by adding synthetic intervals when the estimated intervals do not span the reference intervals or otherwise trimming estimated intervals.

%this affects___

\subsection{Segment Normalized Conditional Entropy Scores}

% When adding intervals, we ensure that the labels do not conflict with existing labels in the estimated annotation.
% This has the effect of changing the normalization constant in the normalized conditional entropy scores.

% When there's only one label, the normalized conditional entropy scores are not well defined.
% In MIREX, they are assigned a score of 1 in this case; in \mireval{} we assign a score of 0.

@@

@@

When a reference melody annotation contains no unvoiced frames, the voicing false alarm rate is not well defined.
MIREX assigns a score of 1 in this case, while \mireval{} assigns a score of 0.
%%%
%%%
%%%
% WHY?
%%%
%%%
%%%
In the data set over which the average relative change for the melody metrics was computed, one reference annotation contained no unvoiced frames.
This discrepancy caused a large inflation of the average relative change reported for the voicing false alarm rate due to the small number of examples in our dataset.

@@
